---
output: github_document
html_preview: false
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  fig.align = "center",
  fig.width = 6,
  fig.height = 6,
  dpi = 300,
  tidy = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/README-"
)
```

## `QSyncR` package
___

This package provides a few simple workflows for cleaning, checking and maintaining [GeoPackage](https://www.geopackage.org/) databases that are used in conjunction with [QGIS](https://qgis.org/) and [QField](https://qfield.org/).

*In development*

To install the package, use [devtools](https://github.com/r-lib/devtools):

```{r Install-QSyncR, eval=FALSE}
devtools::install_github("mottensmann/QSyncR")
```

Load the package once installed:

```{r load-QSyncR, warning=FALSE, results='hide'}
library(QSyncR)
```

## Functions

### `sync`: Handle duplicated data

Allows to solve duplicate entries after merging file versions. Duplicates are identified based on sharing the same `uuid`. If differences exist, the most recent version is picked based on a attribute representing the time stamp of most recent changes (e.g. `mtime`).

```{r}
## Load two versions of the same layer to merge
dfv1 <- sf::read_sf('~/GIS/QField/Test/Avifauna.gpkg', 'Aves')
dfv2 <- sf::read_sf('~/GIS/QField/Test/Avifauna_v20260413085858.gpkg', 'Aves')
```

`dfv1` contains `r nrow(dfv1)` datapoints, and `dfv2` contains `r nrow(dfv2)`. Next the two data frames are merged and conflicts are summarised.

```{r}
## merge data ...
library(magrittr)
df.merged <- rbind(dfv1, dfv2) %>% 
  ## keep unique rows
  unique.data.frame()

## Show new entries df1
dplyr::filter(dfv1, !uuid %in% dfv2[["uuid"]]) %>% 
  as.data.frame() %>% 
  subset(., select = c(KUERZEL, MTIME, uuid)) %>% 
  head()

## Show conflicts
dplyr::filter(df.merged, uuid %in% df.merged[["uuid"]][duplicated(df.merged[["uuid"]])]) %>% 
  as.data.frame() %>% 
  subset(., select = c(KUERZEL, MTIME, uuid)) %>% 
  dplyr::arrange(uuid) %>% 
  head()
```
 

Now, conflicts are solved using function `sync`:

```{r}
## handle duplicates
df.resolved <- sync(DF = df.merged, UUID = 'uuid', MTIME = 'MTIME')

## export to gpkg
sf::st_write(df.resolved, 
             dsn = '~/GIS/QField/Test/Avifauna_new.gpkg',
             layer = 'Aves',
             layer_options = "OVERWRITE=YES",
             append = FALSE)
```

### `VACUUM`: Reduce Geopackage file size

[SQLite](https://sqlite.org/), the underlying database format for `GeoPackage`, does *not* release unused space back to the filesystem by default. Hence, there is the need to *VACUUM* the database in or to reclaim space. This is especially useful when, for example many features where deleted and the file size remained more or less constant.

```{r}
## Example 
VACUUM(dsn = '~/GIS/QField/Test/Avifauna_new.gpkg')
```

### `download_raster`

Small helper function to query raster data (e.g. orthophtos) in a batch mode.

```{r, eval=FALSE}
## NOT RUN
url = c('https://dop20-rgb.s3.eu-de.cloud-object-storage.appdomain.cloud/324565774/2017-03-24/dop20rgb_32_456_5774_2_ni_2017-03-24.tif',
        'https://dop20-rgb.s3.eu-de.cloud-object-storage.appdomain.cloud/324525776/2014-05-03/dop20rgb_32_452_5776_2_ni_2014-05-03.tif')
download_raster(url, filename = basename(url), dest = "output_folder")
```
