---
output: github_document
html_preview: false
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  fig.align = "center",
  fig.width = 6,
  fig.height = 6,
  dpi = 300,
  tidy = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "inst/README-"
)
```

## `GeoPackageR` package
___

This package provides a few simple workflows for cleaning, checking and maintaining [GeoPackage](https://www.geopackage.org/) databases that are used in [QGIS](https://qgis.org/).

*In development*

To install the package, use [devtools](https://github.com/r-lib/devtools):

```{r Install-GeoPackageR, eval=FALSE}
devtools::install_github("mottensmann/GeoPackageR")
```

Load the package once installed:

```{r load-GeoPackageR, warning=FALSE, results='hide'}
library(GeoPackageR)
```

## Functions

### `shrink_gpkg`

[SQLite](https://sqlite.org/), the underlying database format for `GeoPackage`, does *not* release unused space back to the filesystem by default. Hence, there is the need to *vacuum* the database in or to reclaim space. This is especially useful when, for example many features where deleted and the file size remained more or less constant.

```{r}
## Example 
shrink_gpkg(dsn = "~/GIS/QField/Backups/Avifauna.gpkg")
```


